Article Title

### 2013-07-29 sections/Theory.tex
Added figure captions.

\subsubsection{Problem setup}

@@

\subsubsection{Bias-variance tradeoff}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum.

@@

With other loss functions, the risk is also an increasing function of the two components, although not generally the sum.

@@

\subsubsection{Evaluation of estimators}
Another popular loss  function for covariance estimation arises from the theory of normal distributions.  Under the assumption of normality  with zero mean, the log likelihood of the covariance matrix $\Sigma$ given the independent sample $z_1,\ldots,z_m$, with $S = \tfrac 1 m \sum\limits_{i=1}^m z_i z_i^\T$,  
\begin{equation}
L\left(\Sigma \mid S\right) = -\tfrac m 2 \ln(2\pi) - \tfrac m 2 \ln \det \Sigma - \tfrac m 2 \Tr(\Sigma^{-1} S)
\end{equation}
Then the Gaussian loss function $\mathcal L_g$ is constructed by rescaling the normal log likelihood and dropping the constant term
\begin{equation}
\begin{split}
\mathcal L_g(\hat S,S) = &-\frac 2 m L\left(S \mid \hat S \right) - \ln(2\pi) 
\\ 
\equiv & \ln \det \hat S + \Tr(\hat S^{-1} S) 
\end{split}
\end{equation}
The corresponding excess loss 
\begin{equation}
\ell_g(\hat S,S) = \mathcal L_g(\hat S,S) - \mathcal L_g(S,S) 
= -\ln \det \left(\hat S^{-1} S\right) + \Tr\left(\hat S^{-1}S\right) - p
\end{equation}
is known as \emph{entropy loss} \citep{James:1961}.

Despite the fact that entropy loss is derived from normal theory, the choice of a loss function is not equivalent to assuming a specific form of $F$. The loss function only measures the distance between the estimate and the true value of a parameter of the true distribution but not the distance between distributions themselves. Minimizing the loss function improves the estimate under any true distribution.

@@

 The two loss functions $\mathcal L_e(\hat S,S)$ and $\mathcal L_g(\hat S,S)$ are particularly suitable for empirical risk estimation thanks to their linearity with respect to $S$ in the sense that 
\begin{equation}
\mathcal L\left(\hat S,\alpha S_1 + (1-\alpha)S_2\right) 
\equiv 
\alpha\mathcal L(\hat\Sigma,S_1) + (1-\alpha)\mathcal L(\hat S,S_2)
\end{equation}
which allows bringing the expectation inside 
\begin{equation}
\mathbb E\left[ \mathcal L\left(\hat\Sigma_r, \hat\Sigma_0(\hat F_m^\prime)\right) \right] 
=
\mathbb E\left[ \mathcal L\left(\hat\Sigma_\gamma, \mathbb E\left[\Sigma_0(\hat F_m^\prime)\right]\right) \right] 
=
\mathbb E\left[ \mathcal L\left(\hat\Sigma_\gamma, \Sigma\right) \right] 
\end{equation}
Then the expectation of the empirical risk is 
\begin{equation}
\mathbb E\left[\hat r_\gamma\right] 
= \mathbb E\left[\mathcal L(\hat\Sigma_\gamma,\Sigma)\right]
= r_\gamma + \mathcal L(\Sigma,\Sigma)
\end{equation}
This means, that our goal of minimizing the true loss $r_\gamma$ can be replaced with minimizing  the empirical loss $\hat r_\gamma$.

@@

\subsubsection{Constructing a regularized estimator}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.

@@

\subsubsection{Optimization of the regularization parameter}
Analytic solutions when exist \citep{Ledoit:2004,Schafer:2005}, nested cross-validation otherwise.

\subsubsection{Interpretation of revealed structure}
Sparseness (dimensionality reduction) are key, but must be supported by data, not emph{ad hoc}. \citep{Fan:2006,Malmersjo:2013}.

\subsubsection{Out choices of regularized covariance estimates}
\begin{enumerate}[\qquad 1.\;\;]
\item sample covariance (benchmark)
\item covariance shrinkage 
\item factor model
\item graphical lasso
\item latent-variable graphical lasso
\end{enumerate}

>>>>

\paragraph{Problem setup:}

@@

\paragraph{Variance-bias tradeoff:}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum.

@@

With other loss functions, the risk is also an increasing function of the two components, although is not generally the sum.

@@

\paragraph{Evaluation of estimators:}
Another popular loss  function for covariance estimation arises from the theory of normal distributions.  Under the assumption of normality  with zero mean, the log likelihood of the covariance matrix $\Sigma$ given the independent sample $z_1,\ldots,z_m$, with $S = \tfrac 1 m \sum\limits_{i=1}^m z_i z_i^\T$,  
\begin{equation}
L\left(\Sigma \mid S\right) = -\tfrac m 2 \ln(2\pi) - \tfrac m 2 \ln \det \Sigma - \tfrac m 2 \Tr(\Sigma^{-1} S)
\end{equation}
Then the Gaussian loss function $\mathcal L_g$ is constructed by rescaling the normal log likelihood and dropping the constant term
\begin{equation}
\begin{split}
\mathcal L_g(\hat S,S) = &-\frac 2 m L\left(S \mid \hat S \right) - \ln(2\pi) 
\\ 
\equiv & \ln \det \hat S + \Tr(\hat S^{-1} S) 
\end{split}
\end{equation}
The corresponding excess loss 
\begin{equation}
\ell_g(\hat S,S) = \mathcal L_g(\hat S,S) - \mathcal L_g(S,S) 
= -\ln \det \left(\hat S^{-1} S\right) + \Tr\left(\hat S^{-1}S\right) - p
\end{equation}
is known as \emph{entropy loss} \citep{James:1961}.

Despite the fact that entropy loss is derived from normal theory, the choice of a loss function is not equivalent to assuming a specific form of $F$. The loss function measures the discrepancy between distribution parameters rather than the distance between distributions. \TODO{explain Bregman divergence?}

@@

 The two loss functions $\mathcal L_e(\hat S,S)$ and $\mathcal L_g(\hat S,S)$ are particularly suitable for empirical risk estimation thanks to their linearity with respect to $S$ in the sense that 
\begin{equation}
\mathcal L\left(\hat S,\alpha S_1 + (1-\alpha)S_2\right) 
\equiv 
\alpha\mathcal L(\hat S,S_1) + (1-\alpha)\mathcal L(\hat S,S_2)
\end{equation}
which allows bringing the expectation inside 
\begin{equation}
\mathbb E\left[ \mathcal L\left(\hat\Sigma_r, \hat\Sigma_0(\hat F_m^\prime)\right) \right] 
=
\mathbb E\left[ \mathcal L\left(\hat\Sigma_\gamma, \mathbb E\left[\Sigma_0(\hat F_m^\prime)\right]\right) \right] 
=
\mathbb E\left[ \mathcal L\left(\hat\Sigma_\gamma, \Sigma\right) \right] 
\end{equation}
Then the expectation of the empirical risk is 
\begin{equation}
\mathbb E\left[\hat r_\gamma\right] 
= \mathbb E\left[\mathcal L(\hat\Sigma_\gamma,\Sigma)\right]
= r_\gamma + \mathcal L(\Sigma,\Sigma)
\end{equation}
This means, that our goal of minimizing the true loss $r_\gamma$ can be replaced with minimizing  the empirical loss $\hat r_\gamma$.

@@

\paragraph{Constructing a regularized estimator:}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.

@@

\paragraph{Optimization of the regularization parameter:}
Analytic solutions when exist \citep{Ledoit:2004,Schafer:2005}, nested cross-validation otherwise.

\paragraph{Interpretation of revealed structure:}
Sparseness (dimensionality reduction) are key, but must be supported by data, not emph{ad hoc}. \citep{Fan:2006,Malmersjo:2013}.

\paragraph{Out choices of regularized covariance estimates:}
\begin{enumerate}[\qquad 1.\;\;]
\item sample covariance (benchmark)
\item linear shrinkage toward identity 
\item linear shrinkage toward a single-factor model.
\item multifactor
\item graphical lasso
\item latent-variable graphical lasso
\end{enumerate}
